% !TeX root = root.tex
% !TeX spellcheck = en_US
\section{Petri Net, Termination and Linear Programming}
\subsection{Task 1}
We can encode the presence of non-decreasing cycles in a linear program as follows:
\begin{equation*}
\begin{array}{ll@{}ll}
\text{Variables:} 	& M_1, M_2, X_1, X_2\\
\text{Subject to:} & M_1 \geq 0\\
										& M_2 \geq 0\\
										& X_1 \geq 0\\
										& X_2 > 0\\
										& M_1 = M_0 + C \cdot X_1\\
										& M_2 = M_1 + C \cdot X_2\\
										& M_2 \geq M_1
\end{array}
\end{equation*}
Here, $C$ is the connectivity matrix, $M_0$ is the initial marking, $M_1$ and $M_2$ are markings and $X_1$ and $X_2$ are vectors that represent the number of times each transition fires.
This means that we can reach the marking $M_1$ from $M_0$ by applying an arbitrary number of transitions and we can reach the marking $M_2$ form $M_1$ by applying at least one transition. Since $M_2 \geq M_1$, there is a non-decreasing cycle.

In the example we have
\begin{align*}
&C = \begin{pmatrix}
-1 & -1 & 0 & 0\\
0 & 1 & -1 & 2\\
0 & 0 & 2 & 3\\
\end{pmatrix}\\
&M_0 = \begin{pmatrix} 1 \\ 0 \\ 1 \end{pmatrix},
M_1 = \begin{pmatrix} 0 \\ 1 \\ 1 \end{pmatrix},
M_2 = \begin{pmatrix} 0 \\ 1 \\ 2 \end{pmatrix}\\
&X_1 = \begin{pmatrix} 0 \\ 1 \\ 0 \\ 0 \end{pmatrix},
X_2 = \begin{pmatrix} 0 \\ 0 \\ 2 \\ 1 \end{pmatrix}.
\end{align*}
For these assignments all constraints are satisfied and a non-decreasing cycle is found.

\subsection{Task 2}
This analysis does not always work. If we look at the following example from the lecture
\begin{center}\begin{tikzpicture}[node distance=1.5cm,>=stealth',bend angle=45,auto]
	\node[place,tokens=0] (0) []{};
	\node [transition] (a) [right of=0]{}
		edge[pre, bend right = 20] node[midway, above]{1} (0)
		edge[post, bend left = 20] node[midway, below]{2} (0);
\end{tikzpicture}\end{center}
and set
\begin{align*}
&C = (1)\\
&M_0 = M_1 = (0), M_2 = (1)\\
&X_1 = (0), X_2 = (1),
\end{align*}
all constraints are satisfied and therefore the linear program finds a non-decreasing cycle. But since in the initial marking the place has no token and the transition can not fire, the petri net actually terminates.

Therefore, the analysis is sound but not complete. If we are allowed to pick the initial marking such that every transition can be fired, the analysis is also complete since we can fire the transitions in the non-decreasing cycle. 