% !TeX root = root.tex
% !TeX spellcheck = en_US
\section{Limits of Binary Session Types}

\subsection{Task 1 Can you find a type for the ping-pong example?}

First we write the ping-pong example as processes.

\[ping(a,b) =^{def} !a.?b.ping(a,b)\]
\[pong(a,b) =^{def} ?a.!b.pong(a,b)\]
\[(\nu~x,y)(ping(x,y)|pong(x,y))\]

Since the ping-pong example is defined recursively, we have to start somewhere, thus we make the assumption $\Gamma \vdash ping(a,b):i_{ab}$ this allows us to conclude based on pongs definition, that $\Gamma \vdash pong(a,b):?a;i_{ba}$.

Now because we know how the example is constructed we need \[\Gamma = \{(ping(x,y),i_{xy}),(pong(x,y),o_{xy})\], with $i_{xy}=^{def}!x;?y;i_{xy}$ and analogously for $o_{xy}=^{def}?x;!y;o_{xy}$

By an argument by induction if $\Gamma(ping(x,y))=dual(\Gamma(pong(x,y)))$.

\subsection{Task 2 Can you find a type for the juggling example}

Since I am not sure how to encode channels other than as a state of the system and thus as a type, I will encode channel contents as types, this just multiplies the number of types we would need by the number of possible channel states.

However, since we want a well typed system $(P:t_1)|(Q:t_2)$, $t_1=dual(t_2)$, meaning when left hand sends, right hand has to receive, however both systems send first, thus unless we non-trivially reformulate our notion of duality or the $\Gamma$-System, it is not possible to type the juggling example.

We could redefine sending, to be dual to anything. And receiving to be dual to having the message in the channel. Then we can define the juggling example as a process of the form

\[sh(a,b)=!b.rh(b,a)\]
\[rh(a,b)=!a.?b.rh(a,b)\]
\[(\nu~r,l)(sh(l,r)|rh(l,r))\]

Now we would have to hide the channels in the types in the sense that, the type of $\Gamma(sh(a,b))=(b).\Gamma(rh(b,a))$, however it is not clear how the types influence each other throughout the execution.

\subsection{Task 3 Can you find an example which can be typed and where the channels may grow unboundedly?}

Overall I do not understand how we are supposed to have duality, but at the same time have channels that interact with each other. Thus I am unable to answer this question.